---
title: "2025-04-29 Testing reticulate"
format: html
---

```{r setup}
library(tidyverse)
library(targets)
library(reticulate)
library(here)

#this is important because this notebook is in a subdirectory of the project
targets::tar_config_set(
  store = here::here("_targets"),
  script = here::here("_targets.R")
)
```

```{r}
config <- tar_read(config)
```

Set up to use the right conda environment.
```{r}
use_condaenv("triangulate")
source_python(here("python", "calibrate_charuco.py"))
```

I tried `map_chr` here also and it didn't change anything
```{r}
vidnames <- 
  with(config, 
     map_vec(calibration_videos, \(fn) list(file.path(base_path, fn)))
  )

vidnames
```
# Testing the python bits

Ultimately these will go in a separate script.
```{python}
board = aniposelib.boards.CharucoBoard(squaresX=r.config['nsquaresx'],
                                        squaresY=r.config['nsquaresy'],
                                        square_length=r.config['square_length'],
                                        marker_length=r.config['marker_length'],
                                        marker_bits=r.config['marker_bits'],
                                        dict_size=r.config['dict_size'])
                                        
camgroup = aniposelib.cameras.CameraGroup.from_names(r.config['camera_names'])
```

Key thing: `calibrate_videos` expects the video names to be an array of arrays (with single values in the sub array). I couldn't figure out how to set this up in the R variable, but it's easy to set it up in Python.
```{python}
# nest the video names in an array
vidnames = [[vn1] for vn1 in r.vidnames]
err, rows = camgroup.calibrate_videos(vidnames, board, 
                            init_intrinsics=True, init_extrinsics=True, 
                            verbose=True)
```

Next step is to test the script.